Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-11-30 paper/reply.tex
Added missing benchmark/engine comparison response

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} Authors' response (Pascal).}
\end{quote}

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} We only state the winning back-end in the
results table, annotating where the one-stage engine was faster. The two order
of magnitudes were measured empirically, since the one-stage engine times out
on the majority of benchmarks.}
\end{quote}

@@

\begin{quote}
\textcolor{blue}{\textbf{Response:} We did include an upper bound for both the
bit width and execution time. Given an arbitrarily high precision and given
unlimited execution time, the engine will always succeed.}
\end{quote}
